Bioverse: Origins of Life

### 2023-08-30 src/tex/ms.tex
Provide a .bib file for co-authors
explicitly mention predictions
develop structure

% Define document class
\documentclass[twocolumn]{aastex631}
\input{preamble}
\begin{document}

@@

\section{Origins of Life Scenarios and their predictions}
\todo[inline]{Present widely discussed OOL scenarios and their predictions on exoplanet observables; derive testable hypotheses.}
\label{sec:ool_scenarios}
In this section, we present some of the most prominent origins of life scenarios and their observational predictions.
We focus on the necessary environmental conditions for the processes and reactions inherent to each scenario, and aim to identify distinct observables that are accessible via present and near-future remote sensing techniques.

@@

@@

@@

@@

@@

\section{Hypothesis tests}
\label{sec:hypotests}
\todo[inline]{Briefly introduce Bayesian model comparison, then present the particular hypotheses in their mathematical form.}
\subsection{H1: Life only originates in hydrothermal vents}

\subsection{H2: Life only originates in subaerial ponds with wet/dry cycles}

\subsection{H3: Life only originates on planets with particular UV irradiance}

@@

\section{Discussion and Conclusions}
\label{sec:discussion}

%''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''

\bibliography{bib}

>>>>

% Define document class
%\documentclass[twocolumn,twocolappendix,linenumbers]{aastex631}
\documentclass[modern,linenumbers]{aastex631}
\input{preamble}
\begin{document}

@@

\section{Origins of Life Scenarios and their Predictions}
\todo[inline]{Present widely discussed OOL scenarios and their predictions on exoplanet observables; derive testable hypotheses.}
\label{sec:ool_scenarios}
In this section, we present some of the most prominent origins of life scenarios and their observational predictions.
We focus on the necessary environmental conditions for the processes and reactions inherent to each scenario, and aim to identify distinct observables that are accessible via present and near-future remote sensing techniques.

@@

\textbf{Prediction:} Planets with high-pressure ices do not show biosignatures.

@@

\textbf{Prediction:} Biosignatures occur outside the tidal locking zone and at bulk densities consistent with exposed rock..

@@

\textbf{Prediction:} Past UV flux and the occurrence of biosignatures are correlated.

@@

\section{Hypothesis Tests}
\label{sec:hypotests}
\todo[inline]{Briefly introduce Bayesian model comparison, then present the particular hypotheses in their mathematical form.}

\subsection{Bayesian hypothesis testing with \bioverse}

\subsection{H1: Life only originates in hydrothermal vents}
The hydrothermal vent scenario does not allow oceans deep enough to form an impenetrable layer of high-pressure ice on its floor.
The resulting allowed parameter space is described by a lower limit on the bulk density. \todo[inline]{+ exclude atmospheric signature for water worlds?}
...

\subsection{H2: Life only originates in subaerial ponds with wet/dry cycles}
We parametrize the required exposed land surface in this scenario as a lower limit in bulk density that is higher than for H1.
Further, the tidal locking timescale of the planet may not be smaller than the age of the system.
...

\subsection{H3: Life only originates on planets with particular UV irradiance}
We test a UV irradiance requirement by relating the occurrence of life on a planet with a minimum past UV flux, which is a function of ...? \todo[inline]{SUKRIT}

\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
This test requires the detection of multiple biosignatures.''
~\\
Test for negative correlations as well?}

@@

@@

\section{Discussion and Conclusions}
\label{sec:discussion}
%''Which natural processes best explain how living matter spontaneously appears from nonliving matter?''~\citep{Malaterre2022}
%WE consider life ``as we know it''

\subsection{What do we learn from a single biosignature detection?}
\todo[inline]{discuss constraining power on OOL of a convincing biosignature detection on a single planet, depending on the position of the planet in the parameter space we explored.}

\subsection{Constraining power for the origins of life as a function of biosignature location}
\todo[inline]{How does the location of biosignature detections impact the credibility of OOL scenarios?}
\todo[inline]{biosignature on M~dwarf planet vs. FGK: Impact on UV flux requirement?}

\subsection{Conclusions and future work}

\bibliography{bib,coauthors}
